\documentclass[11pt,a4paper]{article}

% Packages
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{datetime2}

% Page setup
\geometry{top=1.5cm,left=1.5cm,right=1.5cm,bottom=1.5cm}
\setlength{\parindent}{0pt}

% Section formatting
\titleformat{\section}{\large\bfseries\color{blue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries}{}{0em}{}

% Lists
\setlist[itemize]{noitemsep,topsep=0pt,leftmargin=1em}

% Contact Information Command
\newcommand{\contact}[5]{
    \begin{center}
        {\Huge \textbf{#1}} \\[8pt]
        #2 \,|\, #3 \,|\, \href{mailto:#4}{#4} \,|\, #5
    \end{center}
    \vspace{0.5cm}
}

% Date command
\newcommand{\todaydate}{\DTMnow}

\begin{document}

%-------------------- HEADING --------------------
\contact{Hendrik Aucamp}
{257 Potter Street, Doomadgee, Queensland}
{0436 027 177}
{hxauc0@eq.edu.au}
{LinkedIn: linkedin.com/in/hennieaucamp}

\vspace{1cm}

%-------------------- DATE --------------------
\todaydate

\vspace{1cm}

%-------------------- RECIPIENT --------------------
[Recipient Name] \\
[Position Title] \\
[School/Organization Name] \\
[Address Line 1] \\
[Address Line 2] \\
[City, State, Postcode]

\vspace{1cm}

%-------------------- GREETING --------------------
Dear [Recipient Name],

\vspace{0.5cm}

%-------------------- OPENING PARAGRAPH --------------------
I am writing to express my strong interest in the Head of Department – Student Services position at [School Name]. With my current experience as HOD Student Services at Doomadgee State School and extensive background in pastoral care and student wellbeing, I am confident in my ability to make a significant contribution to your student services team.

%-------------------- EXPERIENCE PARAGRAPH --------------------
My current role as HOD Student Services has provided me with comprehensive experience in leading student wellbeing initiatives for Prep to Year 10. I manage student support programs including pastoral care and behavioral support, while collaborating with school leadership to implement strategic student welfare projects. My experience as Dean of Senior Boys at Glenden State School further demonstrates my ability to provide effective pastoral care and student welfare support across diverse year levels.

%-------------------- SKILLS PARAGRAPH --------------------
I bring strong leadership skills in educational management, including curriculum development, staff mentoring, and policy implementation. My experience coordinating student support services and developing partnerships with families, external agencies, and community organizations has equipped me with the communication and problem-solving skills essential for effective student services leadership. Additionally, my role as Chairman of the WH\&S committee demonstrates my commitment to ensuring student and staff safety protocols.

%-------------------- EDUCATION PARAGRAPH --------------------
I am currently pursuing a Master of Education in Inclusion and Special Education at the University of New England, which aligns perfectly with the requirements of this position. My Higher Diploma in Education and Further Diploma in Educational Management provide a solid foundation in educational leadership and student services management.

%-------------------- CLOSING PARAGRAPH --------------------
I am passionate about creating inclusive, supportive learning environments and improving student support systems. My experience in remote and Indigenous community education contexts, combined with my commitment to continuous professional development, makes me an ideal candidate for this role. I am excited about the opportunity to contribute to your school's student services team and make a positive impact on student outcomes and wellbeing.

%-------------------- SIGNATURE --------------------
\vspace{1cm}
Sincerely, \\
\vspace{0.5cm}
Hendrik Aucamp

\end{document}
